Essays in \\Computational Management Science

### 2018-04-25 FrontBackmatter/Abstract.tex
Abstract and acnowledgments (incomplete).

\chapter*{Abstract}
Short summary of the contents in English\dots

>>>>

\chapter*{Abstract}

This thesis presents three specific, self-contained, scientific papers in the Computational Management Science area.
Modern management and high technology interact in multiple, profound, ways. Professor Andrew Ng tells students at Stanford’s Graduate School of Business that ``AI is the new electricity'', as his hyperbolic way to emphasize the potential transformational power of the technology.

The first paper is inspired by the possibility that there will be some form of purely digital money and studies distributed ledgers, proposing and analyzing Hathor, an alternative architecture towards a scalable cryptocurrency.

The second paper may be a crucial item in understanding human decision making, perhaps, bringing us a formal model of recognition-primed decision. Lying at the intersection of cognitive psychology, computer science, neuroscience, and artificial intelligence, it presents an open-source, cross-platform, and highly parallel framework of the Sparse Distributed Memory and analyzes the dynamics of the memory with some applications.

Last but not least, the third paper lies at the intersection of marketing, diffusion of technological innovation, and modeling, extending the famous Bass model to account for users who, after adopting the innovation for a while, decide to reject it later on.

### 2018-04-25 FrontBackmatter/Acknowledgments.tex
Abstract and acnowledgments (incomplete).

I must, first and foremost, give thanks for the complete and unwavering support and love from all my family. My beloved wife Patrícia, my wonderful parents Reynaldo and Angelina, my lovely sister Flávia, my sweet grandmas Geny and Rosaria, and all others who will always be remembered in my heart. Thank you for your patience and for understanding that I was physically far away but very close in heart. A special thanks to my dad, Reynaldo, who always taught me about life and who first awakened my passion for technology and engineering.

Thanks to my wife, Patrícia, for sharing the dreams, the passion, and the craziness, for all her caring and love; and for discussing about this work over and over again. Especially, for understanding my absence.

Thanks to my awesome advisor, Alexandre Linhares, who became a dear friend during this journey.

Thanks to my dear friends Daniel Chada, Layla Mendes, Renato Kogeyama, Luiz Sacramento, Kaillen Givigi, Jamil Chivitarese, Lucia Barros, Daniel Modenesi, André Luiz, Bernardo Machado, always available for serious talking, laughing, and sharing their wide and deep knowledge, even at lunchtime and weekends.

Thanks to Celene.

Thanks to Claudio Abreu.

Thanks to professor Luiz Antônio Joia, who trusted me in the first place. Additionally, thanks to EBAPE / FGV for their excellent teachers and infrastructure.

>>>>

I must, first and foremost, give thanks for the complete and unwavering support and love from all my family. My beloved wife Patrícia, my wonderful parents Reynaldo and Angelina, my lovely sister Flávia, my sweet grandmas Geny and Rosaria, and all others who will always be remembered in my heart. Thank you for your patience and for understanding that I was physically far away but very close in heart. A special thanks to my dad, Reynaldo, who always inspired me and who first awakened my passion for technology and engineering.

Thanks to my wife, Patrícia, for sharing the dreams, the passion, and the craziness, for all her caring and love. Especially, for understanding my absence.

I'm very grateful for the friendship, guidance, and invaluable help of my advisor Alexandre Linhares. Without him this work would never be possible. His passion for cognitive sciences, artificial intelligence, and economics has influenced everyone around him. His ideas have profoundly influenced my thoughts and my life since we have met. I must not forget his wife Paula, who became a dear friend and has always supported me as well, even when I was working in her living room until the sunrise. Thank you for this amazing journey, my friends.

Thanks to my dear friends Daniel Chada, Layla Mendes, Renato Kogeyama, André Luiz, Luiz Sacramento, Kaillen Givigi, Jamil Chivitarese, Lucia Barros, Daniel Modenesi, Bernardo Machado, always available for serious talking, laughing, and sharing their wide and deep knowledge, even at lunchtime and weekends. I will never forget our all-you-can-eat adventures in Bros restaurant, the snacks in Catarina, and the drinks in Bigode bar. You have become close friends who I will carry for life.

Thanks to my long-time partner and dear friend Claudio Abreu, who always encouraged me to take risks and to improve myself. He is the most fearless person I have ever met.

Thanks to EBAPE / FGV for their great faculty, staff, and infrastructure. A special thanks to Celene Silva Melo for her empathy and support besides all the help with paperwork, funding, and many other things. Another special thanks to doctor Luiz Antônio Joia, who trusted me in the first place and guided my first steps into the world of academy.
